Appendix A: Stochastic simulations of noisy phenomena

### 2017-11-01 appendixA/appendixA.Rmd
test fonts on Drone
one more go at registering roboto font embedding in Drone

```{r libraries, cache=FALSE}
library(nimble)
library(RcppRoll)
library(regimeshifts) ## devtools::install_github("cboettig/regimeshifts")
library(adaptivetau)
library(tidyverse)
library(ggthemes)
library(gridExtra)
colours <- ptol_pal()(2)
```

```{r echo=FALSE, cache=FALSE}
## plot themes, non-essential. Comment out if theme creates trouble with fonts on your system.
library(Cairo)
library(hrbrthemes)
library(extrafont)
#extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
hrbrthemes::import_roboto_condensed()   # One-time use to set up fonts

#d <- read.csv(extrafont:::fonttable_file(), stringsAsFactors = FALSE)
#d[grepl("Light", d$FontName), ]$FamilyName <- "Roboto Condensed Light"
#write.csv(d, extrafont:::fonttable_file(), row.names = FALSE)

extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

>>>>

```{r libraries, cache=FALSE}
library(nimble)
library(RcppRoll)
library(regimeshifts) ## devtools::install_github("cboettig/regimeshifts")
library(adaptivetau)
library(tidyverse)
library(ggthemes)
library(gridExtra)
ggplot2::theme_set(theme_bw())
colours <- ptol_pal()(2)
```

```{r echo=FALSE, cache=FALSE, eval=TRUE}
## plot themes, non-essential. Comment out if theme creates trouble with fonts on your system.
library(Cairo)
library(hrbrthemes)
library(extrafont)
extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
hrbrthemes::import_roboto_condensed()   # One-time use to set up fonts

d <- read.csv(extrafont:::fonttable_file(), stringsAsFactors = FALSE)
d[grepl("Light", d$FontName), ]$FamilyName <- "Roboto Condensed Light"
write.csv(d, extrafont:::fonttable_file(), row.names = FALSE)

extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
hrbrthemes::import_roboto_condensed()   # One-time use to set up fonts 
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```
